Optimal (Multiway) Spatial Joins

### 2024-05-28 msj.tex
yufei

Construct
\myeqn{
    R_i' &=& \set{r' \mid r \in R_i \text{ and its trimmed rectangle $r'$ exists}}. \nn
}
Computing the ``segment $h_1$'' for each $r \in R_i$ is an instance of Problem $\mathscr{D}$ (the find-lowest version, with $H$ and $R_i$ as the input). By symmetry, so is the computation of $h_2, v_1$, and $v_2$ segments for each $r \in R_i$. It thus follows from Section~\ref{sec:bricks} that $R_1', R_2', ..., R_{k-2}'$ can be produced in $O(kn \log n)$ total time.

@@

\noindent {\underline{\em Example 4.3.} Let us examine, in turn, the two 2-tuples $\bm{t}_1 = (\alpha', \beta_1')$ and $\bm{t}_2 = (\alpha', \beta_2')$ in $\J(R_1', R_2')$. For $\bm{t}_1$, $B_{\bm{t}_1}$ is the rectangle \ttt{ABCD} in Figure~\ref{fig:hv:type1:ex}c, and $\gleft(\bm{t}_1) = \gbot(\bm{t}_1) = \alpha'$. Accordingly, $\dcross_H(\bm{t}_1) = \set{h_2}$ and $\dcross_V(\bm{t}_1) = \set{v_3}$. For $\bm{t}_2$, $B_{\bm{t}_2}$ is the rectangle \ttt{AEFG}, and $\gleft(\bm{t}_1) = \gbot(\bm{t}_1) = \alpha'$. Accordingly, $\dcross_H(\bm{t}_2) = \set{h_2, h_4, h_5}$ and $\dcross_V(\bm{t}_1) = \set{v_3, v_4, v_5}$.
\qed

@@

\extraspacing {\underline{\em Example 4.4.} In our running example, the $\J^*$ computed includes 10 tuples: $(\alpha, \beta_1, h_2, v_3)$, and $\{\alpha\} \times \{\beta_2\} \times \set{h_2, h_4, h_5} \times \set{v_3, v_4, v_5}$. All these 10 tuples belong to $\J(R_1, R_2, H, V)$ and include the 4 tuples in $\J_1$ (see Example 4.1).
\qed

>>>>

Construct
\myeqn{
    R_i' &=& \set{r' \mid r \in R_i \text{ and its trimmed rectangle $r'$ exists}}. \nn
}
Computing the ``segment $h_\bot$'' for each $r \in R_i$ is an instance of Problem $\mathscr{D}$ (the find-lowest version, with $H$ and $R_i$ as the input). By symmetry, so is the computation of $h_\top, v_\vdash$, and $v_\dashv$ segments for each $r \in R_i$. It thus follows from Section~\ref{sec:bricks} that $R_1', R_2', ..., R_{k-2}'$ can be produced in $O(kn \log n)$ total time.

@@

\noindent {\underline{\em Example 4.3.} Let us examine, in turn, the two 2-tuples $\bm{t}_1 = (\alpha', \beta_1')$ and $\bm{t}_2 = (\alpha', \beta_2')$ in $\J(R_1', R_2')$. For $\bm{t}_1$, $B_{\bm{t}_1}$ is the rectangle \ttt{ABCD} in Figure~\ref{fig:hv:type1:ex}c, and $\gleft(\bm{t}_1) = \gbot(\bm{t}_1) = \alpha'$. Accordingly, $\dcross_H(\bm{t}_1) = \set{h_2}$ and $\dcross_V(\bm{t}_1) = \set{v_3}$. For $\bm{t}_2$, $B_{\bm{t}_2}$ is the rectangle \ttt{AEFG}, and $\gleft(\bm{t}_2) = \gbot(\bm{t}_2) = \alpha'$. Accordingly, $\dcross_H(\bm{t}_2) = \set{h_2, h_4, h_5}$ and $\dcross_V(\bm{t}_2) = \set{v_3, v_5}$.
\qed

@@

\extraspacing {\underline{\em Example 4.4.} In our running example, the $\J^*$ computed includes 7 tuples: $(\alpha, \beta_1, h_2, v_3)$, and $\{\alpha\} \times \{\beta_2\} \times \set{h_2, h_4, h_5} \times \set{v_3, v_5}$. All these 7 tuples belong to $\J(R_1, R_2, H, V)$ and include the 4 tuples in $\J_1$ (see Example 4.1).
\qed
